Initial Analysis

### 2019-09-17 Initial_Analysis.Rmd
Changes in paths

# Determine forlder for saving results
Folder <- "Trans_Results"
Results_Path <- paste(Data_Path,"Results/",Jurisdiction,"/",Folder,sep = "/")

if(file.exists(Results_Path) == TRUE){
  Results_Path <- paste(Data_Path,"Results/",Jurisdiction,"/",Folder,sep = "")
}else{
  dir.create(paste(Data_Path,"Results/",Jurisdiction,"/",Folder,sep = ""))
  Results_Path <- paste(Data_Path,"Results/",Jurisdiction,"/",Folder,sep = "")
}

@@

# Load neighbours data from previouse routine
Neighbours_Data <- read_excel(paste(Data_Path,"Spatial_Data/EEZ_Neighbours_List.xlsx", sep =""))

>>>>

# Determine forlder for saving results
Folder <- "Trans_Results"
Results_Path <- paste(Data_Path,"Results/",Jurisdiction,"/",Folder,"/",sep = "")

if(file.exists(Results_Path) == TRUE){
  Results_Path <- paste(Data_Path,"Results/",Jurisdiction,"/",Folder,"/",sep = "")
}else{
  dir.create(paste(Data_Path,"Results/",Jurisdiction,"/",Folder,"/",sep = ""))
  Results_Path <- paste(Data_Path,"Results/",Jurisdiction,"/",Folder,"/",sep = "")
}

@@
